% Created 2017-10-26 Thu 17:29
\documentclass[9pt, b5paper]{article}
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{xeCJK}
\setCJKmainfont[Boldfont = STSong SC Black, ItalicFont = STKaiti]{STSong}
\setCJKsansfont{STHeiti}
\setCJKmonofont{STFangsong}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{float}
\usepackage{textcomp}
\usepackage{geometry}
\geometry{left=0.1cm,right=0.1cm,top=0.1cm,bottom=0.1cm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{latexsym}
\usepackage{natbib}
\usepackage{listings}
\usepackage{minted}
\usepackage[xetex,colorlinks=true,CJKbookmarks=true,linkcolor=blue,urlcolor=blue,menucolor=blue]{hyperref}
\author{deepwaterooo}
\date{\today}
\title{Emacs Configuration}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.2.1 (Org mode 8.2.7c)}}
\begin{document}

\maketitle
\tableofcontents


\section{Updates}
\label{sec-1}
\begin{itemize}
\item Remove not frequently used bothering commands from syslog-mode, and define simplified customized macro command for android SDK log analysis.
\item \textbf{Enhanced syslog-mode}, with simplified textile-mode feature integrated for personal debugging log viewing propose. Will continuously improve relative features.
\item logview-mode, log4j-mode, syslog-mode, in progress, so far only syslog-mode works, needs to combine textile-mode functions/hooks.
\item textile-mode for android logs;
\item sr-speedbar set fixed hight and width cater to current project file names length;
\item fixed previously existing tab cannot indent line and region problem;
\item company mode works convenient and as I expected;
\item C-c f formating files according to needs. Fix minor bugs for java python csharp-mode swift-mode auto complete.
\item clean auto-complete-mode, made repository more consistant.
\item csharp-mode: fixed minor bugs for autopairing, as well as expand \{\} for function scope.
\item swift-mode using swift3
\item org-mode src code highlight is on, just I forgot to specify language before.
\item emacs key-bound for mac keyboard, so that it would be convenient for me to type some specific keys. 
\begin{itemize}
\item exchanged the position of \^{}Control and Capslock;
\item exchanged the position of Option and Command keys;
\item through mac system preference.
\item I tried this yesterday, but after having used window's keyboard for all these years for emacs, it is still very difficult to get used to the mac keyboard even after key exchanges.
\item changed keyboard today actually so that I could type more conveniently.
\end{itemize}
\item other major-modes, for example: \textbf{java-mode}, \textbf{csharp-mode}, which I would need to use pretty soon, is ready for use now (auto-complete + yasnippet etc).
\item All the minor warnings, warning messages when starting emacs, modes fixes are all fixed, a clean Emacs open ready for work.
\end{itemize}

\section{starting point}
\label{sec-2}
\begin{itemize}
\item It is a new computer, and I did try to git clone from my own repository to new laptop, but after fixed errors and tried, \textbf{I promise I do NOT and can NOT bare the out-dated emacs 22.X any more, I have to move on.} I have to install newer versions for my own later on convenience.
\item Instead of configuring my own again, this time, I tried from some "big" person's repository and try to make it work on my laptop (fixing errors, installing necessary packages etc), as well as comment out some complicated modes and customization so that I would still be able to use and like my current emacs interface.
\item It is the first time I tried from some big person's (or any person's configurature completely), it was tidious to fix all the errors at beginning (I spent more than 2 days on it last week. For me it just took too much time), but so far I like some of the features that had been annoying me before, but I have not and was not able to find good solutions to solve it, like how to auto-complete words when in scripte comment line or in quotes. I like these detailed features which I did try by writing my own snippets from yasnippet mode before.
\item So far, org-mode is not perfect, but it is a fully functional one that I could use and help convenient a game developer's daily work.
\item Will devote more time to understand emacs better, and to solve my own problems and make it more convenient for me to use when I need some specific features.
\end{itemize}

\section{TODOs}
\label{sec-3}
\begin{itemize}
\item get cmake work later, not urgent though.
\item babel org-mode so I don't have to copy from specific babeled source org-mode files in order for chinese characters to work.
\end{itemize}

\section{References}
\label{sec-4}
\begin{itemize}
\item \url{https://github.com/redguardtoo/emacs.d}
\end{itemize}
% Emacs 25.2.1 (Org mode 8.2.7c)
\end{document}